Normalization by Evaluation for Sized Dependent Types

### 2017-02-27 nbe/icfp17.tex
[ ICFP 17 ] Some polishing around the Agda code.
[ ICFP 17 ] Acknowledgements (not printed).

\section{Size irrelevance in practice}
\label{sec:informal}

@@

\section{Syntax}
\label{sec:syntax}

@@

\section{Semantics}
\label{sec:sem}

@@

\section{Soundness  of NbE}
\label{sec:soundnbe}

@@

\section{Algorithmic subtyping}
\label{sec:asub}

@@

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
  This material is based upon work supported by the
  \grantsponsor{GS100000001}{National Science
    Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
  No.~\grantnum{GS100000001}{nnnnnnn} and Grant
  No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
  conclusions or recommendations expressed in this material are those
  of the author and do not necessarily reflect the views of the
  National Science Foundation.
\end{acks}

@@

%% Appendix
\appendix
\section{Appendix}

Text of appendix \ldots

>>>>

\section{Size Irrelevance in Practice}
\label{sec:informal}

In this section, we show how the lack of size irrelevance prevents us from reasoning naturally about programs involving sized types in Type Theory.  We focus on Agda, the only mature implementation of Type Theory with an experimental integration of sized types.

@@

\section{A Type System WIth Irrelevant Size Application}
\label{sec:syntax}

@@

\section{Semantics and Completeness of Normalization by Evaluation}
\label{sec:sem}

@@

\section{Soundness  of Normalization by Evaluation}
\label{sec:soundnbe}

@@

\section{Algorithmic Subtyping}
\label{sec:asub}

@@

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
  This material is based upon work supported by the
  Swedish Research Council (Vetenskapsr\aa{}det)
  under Grant
  No.~621-2014-4864 \emph{Termination Certificates for Dependently-Typed Programs and Proofs via Refinement Types}.
  The first author is grateful for recent discussions with Thierry Coquand, Nils Anders Danielsson, and Sandro Stucki
  which helped clarifying the thoughts leading to this work.
  He also acknowledges past discussions with Christoph-Simon Senjak.
\end{acks}

@@

% %% Appendix
% \appendix
% \section{Appendix}

% Text of appendix \ldots
